\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    #2 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\vspace*{-44pt}
\begin{center}
  \textbf{\LARGE Shaanil Punglia}\\[4pt]
  \href{mailto:shaanil.punglia@icloud.com}{shaanil.punglia@icloud.com} $|$ +91-90220 65354
\end{center}
\vspace{-20pt}

%-----------EDUCATION-----------------
\section{Education}
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Birla Institute of Technology and Science} & Goa, India \\
    \textit{\small Bachelor of Engineering in Electronics \& Instrumentation $\cdot$ GPA: 7.6/10 (First Division)} & \textit{\small Aug 2020 -- July 2024} \\ \\
  \end{tabular*}
  \vspace{-20pt}

%--------TECHNICAL SKILLS------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, R, SQL, Bash, Java, C++} $|$ \textbf{Technologies}{: AWS, Docker, FastAPI, Databricks, PySpark, MLflow} \\
     \textbf{ML/Data}{: PyTorch, HuggingFace, Scikit-learn, Pandas, NumPy, Optuna} $|$ \textbf{Databases}{: PostgreSQL, Redshift, MongoDB} \\
    }}
  \resumeSubHeadingListEnd
  \vspace{-12pt}

%-----------RESEARCH AND PUBLICATIONS-----------------
\section{Research and Publications}
  \resumeSubHeadingListStart
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small Hybrid Deep Learning for Winter Wheat Yield Prediction} & \\
        \textit{\small Under review at EAAI (Elsevier, Q1) $\cdot$ Advisor: Prof. Manogna R.L., BITS Pilani} & \textit{\small Submitted 2025} \\
    \end{tabular*}\vspace{-5pt}
      \resumeItemListStart
        \resumeItem{}
          {Developed a CNN-BiLSTM architecture with self-attention that achieved 81\% R\textsuperscript{2} for wheat yield forecasting across India's Wheat Belt, processing NASA POWER climate data, ISRIC soil profiles, and MODIS-derived vegetation indices.}
        \resumeItem{}
          {Conducted extensive ablation studies across 8 model variants validating each architectural component's contribution, implemented in PyTorch with Optuna-based Bayesian optimization (5000+ trials) achieving MAE of 265 kg/ha, with temporal attention weight analysis identifying November sowing as the critical predictive period.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-10pt}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\small Motilal Oswal Financial Services, \textmd{Machine Learning Engineer}}{\small \textit{Mumbai, India} $\cdot$ \textit{Sep 2024 -- Present}}
      {}{}
      \resumeItemListStart
        \resumeItem{t-GNN for Stock Prediction}
          {Developed a temporal Graph Neural Network (GRU-GNN) in PyTorch Geometric to model the NIFTY 500 index, achieving 67\% precision in predicting downward price movement, outperforming LSTM/XGBoost baselines.}
        \resumeItem{Multi-modal Forecasting}
          {Developed multi-modal stock trend forecasting model integrating FinBERT-processed sentiment features with LSTM temporal modeling, achieving 8\% accuracy improvement over baseline LSTM for weekly trend classification of NIFTY500.}
        \resumeItem{Lip Sync Model}
          {Architected cross-attention mechanism in U-Net decoder of audio-conditioned latent diffusion model to integrate reference frame guidance, fine-tuning on Indic language speech-video pairs to achieve 2x improvement in lip-sync confidence scores.}
        \resumeItem{Text-to-Video Pipeline}
          {Deployed scalable text-to-video generation pipeline on AWS integrating TTS, gesture synthesis, and lip-syncing.}
      \resumeItemListEnd

    \resumeSubheading
      {\small UBS, \textmd{Quant Risk Analyst Intern}}{\small \textit{Mumbai, India} $\cdot$ \textit{Jan 2024 -- July 2024}}
      {}{}
      \resumeItemListStart
        \resumeItem{Credit Risk Model Recalibration}
          {Refined corporate credit risk models (Recovery Ratios, CDS-Implied Rating) in R by integrating systemic volatility factors from the Credit Suisse merger, re-estimating key parameters to safeguard the valuation of a \$450B+ credit book.}
        \resumeItem{Model Validation \& Analysis}
          {Substantiated proposed model updates through rigorous statistical back-testing, proving full compliance with Basel III capital frameworks and securing implementation approval from Model Risk Management (MRMC).}
          
      \resumeItemListEnd

    \resumeSubheading
      {\small Income Tax Department, Govt. of India, \textmd{Data Analyst Intern}}{\small \textit{Remote} $\cdot$ \textit{Aug 2023 -- Dec 2023}}
      {}{}
      \resumeItemListStart
        \resumeItem{Transfer Pricing Surveillance System}
          {Built an automated transfer pricing compliance system using Python to process inter-company transactions, implementing z-score and IQR-based anomaly detection algorithms on corporate filings and industry benchmark data.}
        \resumeItem{Interactive Dashboard}
          {Developed interactive Plotly Dash dashboard with drill-down capabilities to visualize flagged BEPS patterns, enabling tax officials to prioritize high-risk cross-border transactions and identify profit-shifting to low-tax jurisdictions.}
      \resumeItemListEnd
    \resumeSubheading
      {\small Securities and Exchange Board of India, \textmd{Market Regulation Intern}}{\small \textit{Mumbai, India} $\cdot$ \textit{Summer 2023}}
      {}{}
      \resumeItemListStart
        \resumeItem{Policy Automation}
          {Contributed to ETL pipeline integrating IBM DB2 warehouse with National Stock Exchange feeds for compliance monitoring of 70M+ daily transactions, and developed automated data validation scripts to flag inconsistencies in HFT colocation arrangements and call-auctions for illiquid scrips, previously reliant on manual spot-checks.}
        
      \resumeItemListEnd

    \resumeSubheading
      {\small PSBLoansin59minutes, \textmd{Data Science Intern}}{\small \textit{Remote} $\cdot$ \textit{Jan 2023 -- April 2023}}
      {}{}
      \resumeItemListStart
        \resumeItem{Credit Scoring Model}
          {Developed an ML credit scoring model using XGBoost to assess MSME loan eligibility, analyzing tax returns (GST, ITR) and 6-month bank statements to automate initial underwriting decisions across 21+ lending partners.}
        \resumeItem{API Integration}
          {Built RESTful APIs using FastAPI to integrate ML predictions with the loan origination system, connecting PostgreSQL (transactional data) and MongoDB (GST/ITR XML files), enabling real-time loan decisioning for 700+ daily applications.}
      \resumeItemListEnd

    

    \resumeSubheading
      {\small State Council of Education Research and Training, Kerala, \textmd{Practice School Intern}}{\small \textit{Remote} $\cdot$ \textit{Summer 2022}}
      {}{}
      \resumeItemListStart
        \resumeItem{Digital Archiving System}
          {Designed automated document management system using Tesseract OCR to digitize and migrate 8,000+ curriculum documents spanning 15 years into MySQL database with full-text indexing and metadata extraction, reducing policy research document retrieval from manual file searches (avg. 2 hours) to sub-second SQL queries.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{-10pt}


%-----------PROJECTS-----------------
\section{Leadership and Activities}
  \resumeSubHeadingListStart
    \resumeSubItem{Co-founder \& Lead, Caboodle (Academic Platform)}
      {Founded and led 5-member team building Caboodle, an integrated academic platform adopted by 83\% of BITS Pilani Goa's 2020 cohort, consolidating study resources and collaborative tools to maintain peer-learning culture during the pandemic.}
    \resumeSubItem{Fundraising Lead, ISKCON Ahmedabad}
      {Led fundraising campaign for ISKCON cow shelter, coordinating volunteer teams and digital outreach initiatives to raise \$70K USD through individual donations, supporting welfare operations for 400+ rescued cattle.}
  \resumeSubHeadingListEnd

%

%-------------------------------------------
\end{document}
